Tree-based

### 2023-12-13 Final Project.Rmd
said hi
changed to hello
heyyy

---
title: "Project #4: Final Project Report: An exploration of Cirrhosis"
output: html_notebook
---

@@

>>>>

---
title: "Project #4: Final Project Report: An exploration of Cirrhosis"
output: html_notebook
---
hello

@@

Cirrohosis is a condition where the liver is scarred and permanently damaged. As this condition, chances of liver failure and liver cancer increase. We are intrested in creating model that can predict stages of Cirrohosis and also death based on certain conditions. We hope our work can be useful in catching Cirrosis earlier on.

### 2023-12-13 Tree.Rmd
heyyy

---
title: "Tree-based"
author: "Mihir Kulkarni"
date: "2023-12-12"
output: html_document
---

@@

```{r}
# Grow Graduate tree via rpart package
rPartStatus <- rpart(
  formula = Status ~ N_Days + Drug + Age + Sex + Ascites + Hepatomegaly + Spiders + Edema + Bilirubin + Cholesterol + Albumin + Copper + Alk_Phos + SGOT + Platelets + Prothrombin + Stage,
  #Lost Triglycerides + 
  data = trainingData,
  method = "class",
  parms = list(split = "information")
  # We did not need to use the control parameters
)

@@

```{r}
# Display rpart.plot ----
# library(rpart.plot)
rpart.plot(
  x = rPartStatus,
  type = 2,
  extra = 101
)
```

@@

```{r}
# Using the rattle package to visualize the tree ----
fancyRpartPlot(
  model = rPartStatus,
  main = NULL,
  sub = NULL
)
```

@@

@@

>>>>

---
title: "Tree-based"
author: "Mihir Kulkarni, Nithika Menon"
date: "2023-12-12"
output: html_document
---

@@

```{r}
# Grow Graduate tree via rpart package
library(rpart)
rPartStatus <- rpart(
  formula = Status ~ N_Days + Drug + Age + Sex + Ascites + Hepatomegaly + Spiders + Edema + Bilirubin + Cholesterol + Albumin + Copper + Alk_Phos + SGOT + Platelets + Prothrombin + Stage + Tryglicerides, 
  data = trainingData,
  method = "class",
  parms = list(split = "information")
  # We did not need to use the control parameters
)

@@

```{r}
# Display rpart.plot ----
 library(rpart.plot)
rpart.plot(
  x = rPartStatus,
  type = 2,
  extra = 101
)
```

@@

```{r}
# Using the rattle package to visualize the tree ----
library(rattle)

fancyRpartPlot(
  model = rPartStatus,
  main = NULL,
  sub = NULL
)
```

@@

library(kableExtra)

@@

library(yardstick)
